Specifying BYOD Policies With Authorisation Logic

### 2016-03-11 paper.tex
spelling mistakes

\title{Specifying BYOD Policies With Authorization Logic}
\titlerunning{Specifying BYOD Policies With Authorization Logic}
\author{
  Joseph Hallett%\inst{1}
  \and
  David Aspinall%\inst{1}
}
\authorrunning{Hallett and Aspinall}

@@

\begin{abstract}
  % State problem
  BYOD policies are imprecisely specified using natural language.
  % Why is it interesting
  This creates ambiguity, may hide specification problems and make comparison harder.
  % What does my solution achieve
  We show how we can use AppPAL (an authorization logic) to formalise three BYOD policies.
  % What follows from solution
  We identify potential problems in all three policies.
  This suggests authorization logic may help in policy specification and enforcement.
\end{abstract}

@@

Logics of authorization are languages used to express permissible actions.
Their uses include access control~\cite{Abadi:2003kta}, and identifying problems in electronic health records~\cite{Becker:2004fi}, amongst other applications.
\emph{AppPAL}~\cite{Hallett:2016vu} instantiates Becker~et~al{.}'s SecPAL~\cite{Becker:2006vh} language to express mobile app installation policies.
It makes use of delegation relationships and uses external constraints to formalise policies.
AppPAL policies define predicates which can affect application installation (isInstallable) or operation;
 they may be enforced by application rewriting or a modified version of the mobile platform security manager.
We believe it has applications to mobile device BYOD policies as well.

We present excerpts from an AppPAL translation of three BYOD policies. 
It is designed to be readable; we introduce the language alongside the BYOD example excerpts from:
    a security policy from the SANS institute to aid companies in developing their own rules~\cite{Guerin:2008we}, 
    an NHS hospital trust~\cite{Kennington:2014tr},
    and a policy used at The University of Edinburgh~\cite{Williamson:2015tr}.
We show how AppPAL can specifiy BYOD policies making them precise, identifying problems and aiding comparison.

@@

Many BYOD policies describe the apps usable in the workplace.
The Edinburgh policy recommends apps come from reputable sources (though the meaning of \emph{reputable} is left undefined). 
The SANS policy uses app black and white lists written by the IT department.
Infact the SANS policy recommends this multiple times in their document.
\begin{lstlisting}[title={\footnotesize\textbf{Edinburgh}:~\itshape ``Only download applications (‘apps’) or other software from reputable sources.''}]
'edinburgh-policy' says Store can-say App isInstallable if Store sells(App), Store isReputable.
\end{lstlisting}
\begin{lstlisting}[title={\footnotesize\textbf{SANS}:~\itshape ``The IT Department maintains a list of allowed and unauthorized applications and makes them available to users on the intranet.''}]
'sans-policy' says 'it-department' can-say App isInstallable.
\end{lstlisting}
\begin{lstlisting}[title={\footnotesize\textbf{SANS}:~\itshape ``Only approved third party applications can be
installed on handhelds. The approved list can be
obtained by contacting the IT department, or should be
available on the intranet.''}]
'sans-policy' says 'it-department' can-say App isInstallable.
\end{lstlisting}
The NHS policy distinguishes between \emph{clinical} and \emph{non-clinical} apps;
    with both requiring approval through a different group before a committee gives final approval.
In practice these rules are irrelevant: no group has ever approved an app: perhaps unsurprisingly since 82\% of Android medical apps have basic privacy concerns~\cite{Blenner:2016ja}.

>>>>

\title{Specifying BYOD Policies With Authorisation Logic}
\titlerunning{Specifying BYOD Policies With Authorisation Logic}
\author{
  Joseph Hallett%\inst{1}
  \and
  David Aspinall%\inst{1}
}
\authorrunning{Hallett and Aspinall}

@@

\begin{abstract}
  % State problem
  BYOD policies are imprecisely specified using natural language.
  % Why is it interesting
  This creates ambiguity, may hide specification problems and make comparison harder.
  % What does my solution achieve
  We show how we can use AppPAL (an authorisation logic) to formalise three BYOD policies.
  % What follows from solution
  We identify potential problems in all three policies.
  This suggests authorisation logic may help in policy specification and enforcement.
\end{abstract}

@@

Logics of authorisation are languages used to express permissible actions.
Their uses include access control~\cite{Abadi:2003kta}, and identifying problems in electronic health records~\cite{Becker:2004fi}, amongst other applications.
\emph{AppPAL}~\cite{Hallett:2016vu} instantiates Becker~et~al{.}'s SecPAL~\cite{Becker:2006vh} language to express mobile app installation policies.
It makes use of delegation relationships and uses external constraints to formalise policies.
AppPAL policies define predicates which can affect application installation (isInstallable) or operation;
 they may be enforced by application rewriting or a modified version of the mobile platform security manager.
We believe it has applications to mobile device BYOD policies as well.

We present excerpts from an AppPAL translation of three BYOD policies. 
It is designed to be readable; we introduce the language alongside the BYOD example excerpts from:
    a security policy from the SANS institute to aid companies in developing their own rules~\cite{Guerin:2008we}, 
    an NHS hospital trust~\cite{Kennington:2014tr},
    and a policy used at The University of Edinburgh~\cite{Williamson:2015tr}.
We show how AppPAL can specify BYOD policies making them precise, identifying problems and aiding comparison.

@@

Many BYOD policies describe the apps usable in the workplace.
The Edinburgh policy recommends apps come from reputable sources (though the meaning of \emph{reputable} is left undefined). 
The SANS policy uses app black and white lists written by the IT department.
In fact the SANS policy recommends this multiple times in their document.
\begin{lstlisting}[title={\footnotesize\textbf{Edinburgh}:~\itshape ``Only download applications (‘apps’) or other software from reputable sources.''}]
'edinburgh-policy' says Store can-say App isInstallable if Store sells(App), Store isReputable.
\end{lstlisting}
\begin{lstlisting}[title={\footnotesize\textbf{SANS}:~\itshape ``The IT Department maintains a list of allowed and unauthorised applications and makes them available to users on the intranet.''}]
'sans-policy' says 'it-department' can-say App isInstallable.
\end{lstlisting}
\begin{lstlisting}[title={\footnotesize\textbf{SANS}:~\itshape ``Only approved third party applications can be
installed on handhelds. The approved list can be
obtained by contacting the IT department, or should be
available on the intranet.''}]
'sans-policy' says 'it-department' can-say App isInstallable.
\end{lstlisting}
The NHS policy distinguishes between \emph{clinical} and \emph{non-clinical} apps;
    with both requiring approval through a different group before a committee gives final approval.
In practice these rules are irrelevant: no group has ever approved an app: perhaps unsurprisingly since 82\% of Android medical apps have basic privacy concerns~\cite{Blenner:2016ja}.
